---
title: "Impact Analysis 2018-2019"
author: "Andrew M. Demetriou"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  html_document:
          toc: true
---

```{r setup, include=FALSE}
library('knitr')        # report generation

library('here')         # file logistics
library('haven')        # importing SPSS .sav files
library('labelled')     # working with SPSS labels

library('dplyr')        # code logistics

library('ggplot2')      # general visualization

library('lavaan')       # SEM
library('lavaanPlot')   # visualizing results

knitr::opts_chunk$set(include = FALSE, echo=FALSE)

#color scheme
ciri_colors <- c('#fe7241', '#ae5944', '#543c4a', '#67444a')
```

```{r}
source(here("SPSS_constructs_formatting_1.0.R"))

T0_constructs_df <- spss_df %>% filter(wave == "T0")
T1_constructs_df <- spss_df %>% filter(wave == "T1")
T2_constructs_df <- spss_df %>% filter(wave == "T1")

rm(spss_df, constructs)
```

```{r}
big_bad_model <- 
  ' NFA =~ NfA_0001 + NfA_0002 + NfA_0003 + NfA_0004
    
    LoC =~ LoC_0001+ LoC_0002 + LoC_0003 + LoC_0004 + LoC_0005 + LoC_0006
    
    Entrskills =~ Entrskills_0001 + Entrskills_0002 +Entrskills_0003 + Entrskills_0004 + Entrskills_0005 + Entrskills_0006 + Entrskills_0007
    
    TfA =~ TfA_0001 + TfA_0002 + TfA_0003 + TfA_0004
    
    NFA ~~ Entrskills
    TfA ~~ Entrskills
    LoC ~~ Entrskills
    TfA ~~ NFA
    LoC ~~ NFA
    TfA ~~ LoC
 '
```

```{r}
big_bad_fit_1 <- cfa(big_bad_model,data=T0_constructs_df, std.lv=TRUE)
fit <- big_bad_fit_1
lavInspect(fit, "optim.gradient")
lavTech(fit, "optim.gradient")


big_bad_fit_2 <- cfa(big_bad_model,data=T0_constructs_df, std.lv=TRUE, bounds =
TRUE)
```


Smith, T. D., & McMillan, B. F. (2001). A Primer of Model Fit Indices in Structural Equation Modeling.
https://files.eric.ed.gov/fulltext/ED449231.pdf

LoC_fit_1_indices[3] is the chisq; [5] is the corresponding p value:
"...tests the null hypothesis of no difference between the proposed model and
the data structure, and good-fitting models should retain the null hypothesis
-criticised because of sensitivity to sample size

[9] is cfi
"CFI is often heralded as a better test of fit than BFI or RNI because it
does not exceed the 0 to 1 range. CFI values of greater than .9 are generally considered to
indicate acceptable levels of model fit"

rmsea:
"Interpretation of RMSEA values is often considered according to the following: 0
= perfect fit; <.05 = close fit; .05 to .08 = fair fit; .08 to .10 = mediocre fit; >.10 = poor fit
(Byrne, 1998)."
rmsea.ci.upper, rmsea.ci.lower, rmsea.pvalue:
"In using these confidence intervals, a null hypothesis (HO: not a close model fit) could be rejected 
in favor of accepting the alternative (HA: close fit) if the entire range of the confidence interval
is less than .05."

```{r}
get_model_fit <- function(model, name){
  #RMSE, accordig to Smith & McMillan 2001
  indices <- c("rmsea.ci.upper", "rmsea.ci.lower", "rmsea", "rmsea.pvalue")
  names <- c("upper", "lower", "rmsea", "pvalue")
  
  #draw complete set of fit indices
  fit_indices <- fitmeasures(model)
  #RMSEA subset as named vector
  fit_subset <- fit_indices[indices]
  #add model name for reference
  fit_subset$model <- name
  #named vector to row in dataframe
  #fit_subset <- fit_subset %>% t() %>% as.data.frame() 
  return(as.data.frame(fit_subset))
}
#model <- big_bad_fit_2
#name <- "big_bad_fit_2"
#round(fit_subset$rmsea.ci.upper, 2)
#t<-get_model_fit(LoC_fit_1, "LoC_fit_1")
```


```{r}
plot_model <- function(model) {
  lavaanPlot(model=model, node_options = list(fontname = "Helvetica"), edge_options = list(color = "grey"), coefs=TRUE, covs=TRUE, stars='latent')
}
#plot_model(big_bad_fit_2)
```

```{r}
print_rmsea <- function(model_fit) {
  paste0("RMSEA is ",
         round(model_fit$rmsea, 3), 
         ", 95% CI: ", 
         round(model_fit$rmsea.ci.lower, 2), 
         ", ", 
         round(model_fit$rmsea.ci.upper, 2), 
         ", p = ", 
         round(model_fit$rmsea.pvalue, 5)
         )
}
#model_fit <- get_model_fit(big_bad_fit_2, "big_bad_fit_2")
print_rmsea(model_fit)
```




