---
title: "Werktuig PPO report"
author: "Andrew M. Demetriou"
date: "6/17/2022"
output: html_document
---

```{r why_setup, include=FALSE}
library('knitr')              # report generation

library('here')               # file logistics

library('tidyverse')          # code logistics
library('dplyr')              # code logistics
library('tidyr')              # pivoting

library('ggplot2')            # general visualization
library('ggdist')             # raincloud plotting
library('gghalves')           # raincloud plotting

library('forcats')            # reorder bars

library('RobustRankAggreg')   # rank analysis

library('naniar')             # missingness analysis

#report options
knitr::opts_chunk$set(include = FALSE, echo=FALSE)
options(scipen=999)

#color scheme
ciri_colors <- c('#fe7241', '#ae5944', '#543c4a', '#67444a')
```

```{r import_data}
data_file_path <- here("data_", "WerktuigPPO |  FebMar")

data_files     <- list.files(data_file_path)

T0_df <- read.csv(paste0(data_file_path, "/", data_files[1]))

#questions <- colnames(T0_df) %>% as.data.frame()

rm(data_file_path, data_files, file_name)
```

# Who are our participants?

In this section, we examine who applied to the instrument. 


#### Job Titles

```{r job_title, include=TRUE}
job_title <- "Wat.is.jouw.professionele.titel."
T0_df[job_title] %>% lapply(., tolower) %>% as.data.frame() %>% count(Wat.is.jouw.professionele.titel.) %>% arrange(desc(n))

rm(job_title)
```
Commonly cited titles were photographer, illustrator, interior designer, followed by some kind of coaching. 

#### How are participants making their income?

```{r}
income_segment <- "Met.welke.activiteit.verdien.je.het.grootste.deel.van.je.omzet."

T0_df[income_segment] %>% lapply(., tolower) %>% as.data.frame() %>% count(Met.welke.activiteit.verdien.je.het.grootste.deel.van.je.omzet.) %>% arrange(desc(n))

rm(income_segment)
```
Design was the most cited answer, followed by writing and photography. A couple participants mentioned making the majority of their earnings with an office job. 

#### Why did participants sign up?

Using robust ranking aggregation (https://academic.oup.com/bioinformatics/article/28/4/573/213339?login=false), we rank the lists that participants indicated as reasons for participating. 

```{r}
reason <- "Waarom.heb.je.je.aangemeld.voor.dit.programma."
participant_id     <- "X."
columns <- c(participant_id, reason)
df <- T0_df[columns]

ranked_lists <- split(df[reason], 1:nrow(df[reason]))

empty_list <- list()

for(i in 1:length(ranked_lists)){
  empty_list[i] <- lapply(ranked_lists[[i]], strsplit, ",")
}

for(i in 1:length(empty_list)){
  empty_list[i] <- lapply(empty_list[[i]], as.character)
}

ranking <- aggregateRanks(glist = empty_list, N = 12) %>% remove_rownames(.)
kable(ranking)

rm(ranked_lists, empty_list, df, i, reason, participant_id, ranking, columns)
```

```{r}
skills <- c("Hoeveel.nadruk.denk.je.dat.er.gaat.worden.gelegd.op..Business.skills..", "Hoeveel.nadruk.denk.je.dat.er.gaat.worden.gelegd.op..Artistieke.skills...", "En.hoeveel.nadruk.denk.je.dat.er.gaat.worden.gelegd.op..Psychologische.skills..")
 
df <- T0_df[skills]
colnames(df) <- c("Business", "Art", "Psychology")

df <- df %>% pivot_longer(cols = c("Business", "Art", "Psychology"), names_to = "Skill", values_to = "Importance")
```


```{r}
df %>%
  ggplot(aes(x=Skill, y=Importance, fill=Skill)) +
    ggdist::stat_halfeye(
      show.legend = FALSE, 
      adjust = 1,  # the breaks / bins of histogram
      width = .5, 
      justification = -.2,
      .width = c(.5, .95)
      ) +
    scale_fill_manual(values=ciri_colors) +
    geom_boxplot(
      show.legend = FALSE,
      width = .12, 
      coef = 0, 
      outlier.color = NA
    )  +
    gghalves::geom_half_point(
      show.legend = FALSE, 
      side="1", 
      range_scale=.1,
      alpha = .45
      ) +
   scale_y_continuous(
     position = "right",
     breaks = seq(0, 10, by = 1),
     labels = seq(0, 10, by=1)
     ) +
  theme_minimal() +
  theme(axis.title.y = element_blank(), axis.title.x = element_blank())

rm(skills)
```
```{r}
missing <- c('Is.er.naast.Business..Artistieke.en.Psychologische.skills.nog.een.soort.skills.die.niet.genoemd.is.en.die.je.wel.erg.belangrijk.vindt..', 'Welke.soort.skills.mis.je.nog.in.de.voorgaande.vragen.en.wil.je.wel.op.focussen.in.de.training.die.je.gaat.doen.')

T0_df[missing]

rm(missing)
```
## income

```{r}
# income variable name
income <- c("Wat.is.je.maandelijkse.omzet.")
# participant ID
ID <- "X."

# working dataframe
income_t0 <- T0_df %>% select(X., Wat.is.je.maandelijkse.omzet.)
colnames(income_t0) <- c("participant_ID", "income")

# response categories
income_t0$income[income_t0$income=="Minder dan €1.000"] <- 1
income_t0$income[income_t0$income=="€ 1.000 - € 1.500"] <- 2
income_t0$income[income_t0$income=="€ 1.500 - € 2.000"] <- 3
income_t0$income[income_t0$income=="€ 2.000 - € 2.500"] <- 4
income_t0$income[income_t0$income=="€ 2.500 - € 3.000"] <- 5
income_t0$income[income_t0$income=="€ 3.000 - € 3.500"] <- 6
income_t0$income[income_t0$income=="€ 3.500 - € 4.000"] <- 7
income_t0$income[income_t0$income=="€ 4.000 - € 4.500"] <- 8
income_t0$income[income_t0$income=="€ 4.500 - € 5.000"] <- 9
income_t0$income[income_t0$income=="Meer dan € 5.000" ] <- 10
income_t0$income <- na_if(income_t0$income, "Gaat je niks aan")

# time measure
income_t0$time <- "T0"

rm(income, ID)
```

```{r}
# in the future this will be 'income_wide'
income_t0$T0 <- income_t0$income

missingness_table <- income_t0 %>%
  select(T0) %>%
  miss_var_summary(order=FALSE)

colnames(missingness_table) <- c("Time", "Number Missing", "Percent Missing")

missingness_table

# upset table requires at least two variables
#income_t0 %>%
#  select(T0) %>%
#  gg_miss_upset()

rm(missingness_table)
```

```{r}
income_t0$income <- income_t0$income %>% as.numeric()

income_t0 %>%
  ggplot(aes(x=time, y=income, fill = time)) +
    ggdist::stat_halfeye(
      show.legend = FALSE, 
      adjust = 1,  # the breaks / bins of histogram
      width = .5, 
      justification = -.2,
      .width = c(.5, .95)
      ) +
  scale_fill_manual(values=ciri_colors) +
      geom_boxplot(
      show.legend = FALSE,
      width = .12, 
      coef = 0, 
      outlier.color = NA
    ) +
    gghalves::geom_half_point(
      show.legend = FALSE, 
      side="1", 
      range_scale=.25,
      alpha = .3
      ) +
     scale_y_continuous(
       position = "right",
       breaks = seq(1, 10, by = 1),
       labels = c(
       "<1000", "1000-1500", "1500-2000", 
       "2000-2500", "2500-3000", "3000-3500", 
       "3500-4000", "4000-4500", "4500-5000",">5000")
     ) +
  theme_minimal() +
  theme(axis.title.y = element_blank(), axis.title.x = element_blank())
```

```{r}
rm(income_t0)
#colnames(T0_df)
```

## constructs

```{r}
percentage_t0 <- T0_df %>% select(X., Welk.deel.van.je.omzet.verdien.je.met.je.creatieve.activiteiten.)
colnames(percentage_t0) <- c("participant_ID", "percentage")
percentage_t0$percentage %>% as.numeric(percentage_t0$percentage)
percentage_t0$time <- "T0"
```

```{r}
percentage_t0 %>% ggplot(aes(x=time, y=percentage, fill=time)) +
    ggdist::stat_halfeye(
      show.legend = FALSE, 
      adjust = 0.10,  # the breaks / bins of histogram
      width = .5, 
      justification = -.2,
      .width = c(.5, .95)
      )  +
  scale_fill_manual(values=ciri_colors[2]) +
      geom_boxplot(
      show.legend = FALSE,
      width = .12, 
      coef = 0, 
      outlier.color = NA
    ) +
    gghalves::geom_half_point(
      show.legend = FALSE, 
      side="1", 
      range_scale=.25,
      alpha = .3
      ) +
  theme_minimal() +
  theme(axis.title.y = element_blank(), axis.title.x = element_blank())
```

