---
title: "Impact Analysis, 'why', 2018-2019"
author: "Andrew M. Demetriou"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  html_document:
          toc: true
---

```{r why_setup, include=FALSE}
library('knitr')        # report generation

library('here')         # file logistics
library('haven')        # importing SPSS .sav files
library('labelled')     # working with SPSS labels

library('dplyr')        # code logistics
library('tidyr')        # pivoting

library('ggplot2')      # general visualization
library('forcats')      # reorder bars

#report options
knitr::opts_chunk$set(include = FALSE, echo=FALSE)

#color scheme
ciri_colors <- c('#fe7241', '#ae5944', '#543c4a', '#67444a')
```

```{r why_import_data}
#SPSS data file path
data_file_path <- here("data_", "2018_2019_")

#create a list of all files
data_files     <- list.files(here("data_", "2018_2019_"))

#read in SPSS files
T0_df <- read_sav(paste0(data_file_path, "/", data_files[3]))
T1_df <- read_sav(paste0(data_file_path, "/", data_files[4]))
T2_df <- read_sav(paste0(data_file_path, "/", data_files[5]))

rm(data_file_path, data_files)
```

```{r why_df}
#variables representing reasons for participating are labelled as follows:
why_vars <- c(paste0("why_000", seq(1,9)), paste0("why_00", seq(10,15)))

#filter dataframe at T0 for the 'why' variables
#where each reason is a column, with a 1 or a 0 indicating whether or not it was selected
why_df   <- T0_df %>% select(why_vars)
#replace NAs with 0s
why_df[is.na(why_df)] <- 0

#'why' items (in English)
why_reasons <- c("To improve my personal skills", 
                   "To increase my income", 
                   "To become a (fulltime) creative entrepreneur", 
                   "To improve my entrepreneurial skills",
                   "To learn more about entrepreneurialism",
                   "To start a (creative) company",
                   "To learn how to better manage my current creative business", 
                   "To better profile myself as an entrepreneur",
                   "To start seeing myself more as an entrepreneur",
                   "Because I'm having difficulty making money from my creativity",
                   "Because I lack business knowhow",
                   "Because the time I spend on business is hurting my creativity",
                   "Because I don't have enough time to develop a long term strategy",
                   "Because I want to put a value on my creativity", 
                   "Other")

# the question labels are formatted differently in the SPSS file:
why_labels <- val_labels(why_df)
```

## Participant Motivations

Here we examine participants' reasons for choosing to attend the seminar series. Participants were asked 'Waarom heb je je aangemeld voor dit programma?", shown the options listed in Figure 1 (originally in Dutch), and were asked to select all that applied. 

```{r why_df_visualization, include=TRUE, fig.align='left', fig.cap="Figure 1.1: Reasons selected for participating in an intervention, translated to English. Percentage indicates the percent of participants that selected the item."}
#function to count and re-arrange by frequency of response
extract_freq <- function (...) {
  why_df %>% count(...) %>% arrange(desc(n))
}

#apply custom function to out frequency dataframe
#this creates a list of tibbles with frequency counts
#one for each reason 'why'
freq_df <- apply(X = why_df, MARGIN=2, extract_freq)

#rename the columns of each item in the list
for(i in 1:length(freq_df)) {
  freq_df[[i]]$Column <- names(freq_df[i])
  names(freq_df[[i]]) <- c("Variable", "n", "Column_name")
}

#merge list items into a single df
freq_df <- do.call(rbind, freq_df) %>% data.frame() %>% select(Column_name,Variable,n)

#only include rows that indicate that the reason was selected
#add a row indicate a percentage based on whether or not the item was selected
freq_df <- freq_df %>% group_by(Column_name) %>% filter(Variable == 1) %>% mutate(percent = round(n/38*100, digits = 1))

#add reasons to datafame translated to English
freq_df$reasons <- why_reasons

#put rows in descending order based on percentage
freq_df$reasons <- factor(freq_df$reasons) %>%
  fct_reorder(freq_df$percent)

#plot results
freq_df %>%
  ggplot(aes(x=reasons, y=percent)) +
  geom_col(fill=ciri_colors[2]) +
  coord_flip() +
  scale_x_discrete("",position = "top") +
  scale_y_continuous("Percentage") +
  theme_minimal()

most_selected_reason <- freq_df %>% filter(percent == max(freq_df$percent))
#most_selected_reason

rm(why_df, why_labels, freq_df, i, why_reasons, why_vars)
```

The most selected reason was "`r most_selected_reason$reasons`", chosen by __`r most_selected_reason$percent`__% of participants. 



```{r important_modules_df, include=TRUE, fig.align='left', fig.cap="Figure 1.2: Self-reported module importance at two time-points. Frequency indicates the number of participants that indicated that the module was the most important at the given time point."}
belang_df <- factor(T0_df$Belang_module, val_labels(T0_df$Belang_module))
belang_df <- data.frame(table(belang_df))
belang_df$module <- names(val_labels(T0_df$Belang_module))
belang_df$time <- "T0"
colnames(belang_df) <- c("belang_df", "frequency", "module", "time")

belang_t2 <- factor(T2_df$Belang_module, val_labels(T2_df$Belang_module))
belang_t2 <- data.frame(table(belang_t2))
belang_t2$module <- names(val_labels(T2_df$Belang_module))
belang_t2$time <- "T2"
colnames(belang_t2) <- c("belang_df", "frequency", "module", "time")

belang_df <- rbind(belang_df, belang_t2)

belang_df$module <- factor(belang_df$module) %>%
  fct_reorder(belang_df$frequency)

belang_df %>%
  ggplot(aes(x=frequency, y=module, fill=time)) +
  geom_col(position = "dodge") +
  scale_fill_manual(values=ciri_colors) + 
  scale_y_discrete("", position = "right") +
  scale_x_continuous("Frequency") +
  theme_minimal()

rm(belang_t2, belang_df)
```

```{r reason_df, include=TRUE}
reason    <- "q0004"
reasons <- T0_df[reason]
kable(reasons, col.names = "Reasons", align = "l", caption="")
#reasons

rm(reasons, reason)
```
