---
title: "Werktuig PPO report"
author: "Andrew M. Demetriou"
date: "6/17/2022"
output: html_document
---

```{r why_setup, include=FALSE}
library('knitr')              # report generation

library('here')               # file logistics

library('dplyr')              # code logistics
library('tidyr')              # pivoting

library('ggplot2')            # general visualization
library('forcats')            # reorder bars

library('RobustRankAggreg')   # rank analysis

#report options
knitr::opts_chunk$set(include = FALSE, echo=FALSE)

#color scheme
ciri_colors <- c('#fe7241', '#ae5944', '#543c4a', '#67444a')
```

```{r import_data}
data_file_path <- here("data_", "WerktuigPPO |  FebMar")

data_files     <- list.files(data_file_path)

T0_df <- read.csv(paste0(data_file_path, "/", data_files[1]))

#questions <- colnames(T0_df) %>% as.data.frame()

rm(data_file_path, data_files, file_name)
```

# Who are our participants?

In this section, we examine who applied to the instrument. 


#### Job Titles

```{r job_title, include=TRUE}
job_title <- "Wat.is.jouw.professionele.titel."
T0_df[job_title] %>% lapply(., tolower) %>% as.data.frame() %>% count(Wat.is.jouw.professionele.titel.) %>% arrange(desc(n))

rm(job_title)
```
Commonly cited titles were photographer, illustrator, interior designer, followed by some kind of coaching. 

#### How are participants making their income?

```{r}
income_segment <- "Met.welke.activiteit.verdien.je.het.grootste.deel.van.je.omzet."

T0_df[income_segment] %>% lapply(., tolower) %>% as.data.frame() %>% count(Met.welke.activiteit.verdien.je.het.grootste.deel.van.je.omzet.) %>% arrange(desc(n))

rm(income_segment)
```
Design was the most cited answer, followed by writing and photography. A couple participants mentioned making the majority of their earnings with an office job. 

#### Why did participants sign up?

```{r}
reason <- "Waarom.heb.je.je.aangemeld.voor.dit.programma."
participant_id     <- "X."
columns <- c(participant_id, reason)
reason_df <- T0_df[columns]

ranked_lists <- split(reason_df[reason], 1:nrow(reason_df[reason]))

empty_list <- list()

for(i in 1:length(ranked_lists)){
  empty_list[i] <- lapply(ranked_lists[[i]], strsplit, ",")
}

#lapply(ranked_lists[[1]], strsplit, ",")


#lapply(ranked_lists, function(x) ranked_lists[[x]])
#lapply(list[[1]], strsplit, ",")
#lapply(ranked_lists, strsplit, ",")
#ranked_lists <- lapply(as.list(reason_df[reason]), strsplit, ",")
#reason_df[1, 2] %>% strsplit(., ",") %>% as.data.frame() %>% mutate(order = seq(1:12))
```